Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1,t2}

### 2024-02-07 article/article.tex
s
update Paper

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

@@

\begin{frontmatter}
\title{Estimating Quantile Regressions with Multiple Fixed Effects
through Method of Moments \tnoteref{t1}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardo.siles@ucb.edu.bo} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

\affiliation[1]{organization={Levy Economics Institute of Bard
College},,postcodesep={}}
\affiliation[2]{organization={Universidad Católica
Boliviana},,postcodesep={}}
\affiliation[3]{organization={World Bank},,postcodesep={}}

@@

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location-scale model can be identified globally, with only a
single parameter (\(q_\tau\)) requiring local estimation, this
estimation approach will be more efficient than the standard quantile
regression model (\citet{zhao2000}). Second, under the assumption that
\(X\gamma\) is strictly positive, the model will produce quantile
coefficients that do not cross (\citet{he1997}).

@@

This estimator of standard errors may prove useful for two reasons.
First, this estimator would be robust to misspecification of the scale
model assumptions, and thus it could be used as an informal test for the
validity of the model assumptions when compared to the GLS-standard
error (Section~\ref{sec-gls}). Second, as shown in the simulation study,
this estimator performs better than GLS-standard errors even if the
model is correctly specified, because of problemes caused when
\(x\hat\gamma\) is not strictly positive.

@@

To show the performance of the extended strategy, we implement a small
simulation study. We consider a simple model with a single explanatory
variable \(x\). In contrast with MSS, we consider a two-way fixed effect
structure that is more general than the panel structure. For this
exercise, we consider the following data-generating process:

\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
\]

where \(\alpha_{1i}\sim \chi^2(1)\), \(\alpha_{2i} \sim \chi^2(1)\), and
\(x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))\), with
\(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
\(\varepsilon_i\) is assumed to follow a centered \(\chi^2\)
distribution.\footnote{Specifically we assume
  \(\varepsilon=\frac{r_i}{5}-1\), where \(r_i\) follows a chi-squared
  distribution such that \(r_i \sim \chi^2(5)\). Simulations under the
  assumption of normal errors are available upon request.} We assume
that there are 50 mutually exclusive groups for each set of fixed
effects. Observations are assigned to each subgroup randomly using a
uniform distribution between 1 and 50. We consider sample sizes of 500,
1000, 2000, and 4000 observations, which implies an average of 10, 20,
40, and 80 observations per group. The model is estimated using the
location-scale model with heteroskedastic linear errors and we report
the coefficients for the 25th and 75th quantiles. We run this excercise
5000 times. Table~\ref{tbl-sim1} reports the bias, simulated standard
error, and mean squared error. We also report the results obtained using
an adaptation bias-corrected estimator based on the split-panel
jackknife estimator proposed by \citet{dhaene2015}.\footnote{For the
  implementation, we first estimate the model using the full sample,
  then randomly assign each observation into one of two groups, and
  finally reestimate the quantile coefficients for each group. The
  bias-corrected estimator is then obtained as
  \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)\).}
These results are labeled JKC.

Similar to the findings in MSS, we find that while the estimator
presents a substantial bias when the sample is small (\(N=500\)), this
bias shrinks as the sample size increases. As MSS describes, the bias
seems to be proportional to the sample size, or more precisely to
\(N/N_{g1}\) and \(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the
average number of observations per group. Interestingly, the
bias-corrected estimator presents an almost 0 bias for the 25th
percentile, even when the samples are small (about 10 observations per
subgroup). In contrast, when considering the 75th percentile, the simple
estimator shows smaller bias than the Jacknife estimator.{[}\^{}88: This
is also consistent with simulations with a single fixed effect{]} In
either case, despite the bias reduction obtained using the JKC
estimator, the standard errors are larger than without correction. For
the 25th quantile, the reduction in bias is large enough to produce a
smaller Mean Squared Error (MSE) than the simple estimator. This is
similar to the results of MSS.

@@

\begin{tabular}{l*{6}{c}cccccccccccc}
\hline
            &     \multicolumn{3}{c}{N = 500}   &     \multicolumn{3}{c}{N = 1000}            \\
            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
\hline
q25         &            &            &            &            &            &            \\
\ mmqreg      &       0.173&       0.233&       0.084&       0.100&       0.155&       0.034\\
\ jkc         &       0.051&       0.278&       0.080&       0.022&       0.170&       0.029\\
\hline
q75         &            &            &            &            &            &            \\
\ mmqreg      &      -0.039&       0.384&       0.149&      -0.003&       0.279&       0.078\\
\ jkc         &       0.067&       0.469&       0.224&       0.033&       0.305&       0.094\\
\hline
            &     \multicolumn{3}{c}{N = 2000}   &     \multicolumn{3}{c}{N = 4000}            \\
            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
\hline
q25         &            &            &            &            &            &            \\
\ mmqreg      &       0.052&       0.107&       0.014&       0.027&       0.074&       0.006\\
\ jkc         &       0.007&       0.113&       0.013&       0.002&       0.077&       0.006\\
\hline
q75         &            &            &            &            &            &            \\
\ mmqreg      &       0.004&       0.195&       0.038&       0.007&       0.138&       0.019\\
\ jkc         &       0.009&       0.204&       0.042&       0.004&       0.141&       0.020\\
\hline
\multicolumn{7}{p{.7\textwidth}}{ \footnotesize Note: mmqreg - The proposed estimator. 
JKC-Jacknife Bias Corrected Estimator. SE- Simulated Standard Error.
MSE - Mean Squared Error. Mean bias is the difference 
between the estimated coefficient and the analytical true value. }\\
\end{tabular}

@@

As described in section Section~\ref{sec-se}, GLS standard errors may
not be appropriate if heteroskedasticity in the model is misspecified.
This could happen if the heteroskedasticity is not linear in parameters
or if there are correlations within groups. To show the performance of
the GLS standard errors, we consider two additional simulations. To see
the impact of heteroskedasticity misspecification, we assume the DGP is
given by

\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
\]

To show the impact of ignoring correlation within groups, we consider
the case where the error \(\varepsilon\) is correlated within groups
defined by the first fixed effect. Specifically:

\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\]

where \(z_i~N(0,1)\) and \(w_g~N(0,1)\), with \(g\) being the \(g_{th}\)
group defined by the first fixed effect.

For the simulation, we run the excercise 5000 times, using a sample of
size \(N=2000\). The results from both simulations are reported in the
Table~\ref{tbl-sim2}. We report the average coefficient,
simulation-based standard errors, and the standard errors using GLS,
robust and clustered estimations.

\begin{longtable}[]{@{}lcccc@{}}
\caption{Heteroskedasticity misspecification and clustered
errors}\label{tbl-sim2}\tabularnewline
\toprule\noalign{}
& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Coefficient & 0.550 & 1.442 & 0.775 & 1.229 \\
SIM\_SE & 0.154 & 0.155 & 0.109 & 0.107 \\
GLS\_SE & 0.476 & 0.451 & 0.288 & 0.221 \\
Robust & 0.140 & 0.139 & 0.087 & 0.088 \\
Cluster & & & 0.097 & 0.097 \\
\end{longtable}

One of the conclusions from the results in Table~\ref{tbl-sim2} is that
the results for the 25th and 75th quantiles are mostly identical,
because of the symmetric error we used in the simulation. On the one
hand, because the error structure is misspecified, we should expect to
see a large bias in the estimated coefficients, especially in cases of
misspecified heteroskedasticity. However, the purpose of this exercise
is not to demonstrate the unbiasedness of the coefficients, but rather
to assess the performance of the standard error estimation.

As expected, the GLS standard errors are biased and the bias is larger
in the case of misspecified heteroskedasticity. In fact, with
heteroskedasticity misspecification, the average GLS-SE (0.476) is
almost three times as large as the simulation-based standard error
(0.154). In this first case, robust standard errors perform better, but
with a small difference (0.14 to 0.154). In the case of clustered
correlation, GLS-SE also performs poorly. Robust standard errors perform
better, but seem to underestimate the magnitude of the true standard
errors. Finally, cluster standard errors perform the best, with a small
difference between the simulation-based standard errors (0.097 to
0.109).

@@

Furthermore, we have assessed the impact of misspecified
heteroskedasticity and intracluster correlation on the performance of
standard error estimations. Our findings emphasize the importance of
using appropriate standard error estimators to ensure accurate
inference. In particular, we find that GLS standard errors are biased
when the model heteroskedasticity is misspecified and that robust and
clustered standard errors perform better in these cases. This may also
suggest a venue for future research, in which the validity of the
location-scale model assumption is tested.

@@

\begin{itemize}
\tightlist
\item
  \texttt{mmqreg} in Stata: `net install mmqreg,
  from(https://friosavila.github.io/stpackages)
\item
  \texttt{mmqreg} in R: Program available in mmqreg repository on GitHub
  (https://github.com/friosavila/mmqreg)
\item
  \texttt{mmqreg} in Python:
\item
  \texttt{mmqreg} in Julia:
\end{itemize}

>>>>

\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
\tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

@@

\begin{frontmatter}
\title{Estimating Quantile Regressions with Multiple Fixed Effects
through Method of Moments \tnoteref{t1,t2}}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[2]{Leonardo Siles%
%
}
 \ead{leonardo.siles@ucb.edu.bo} 
\author[3]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

\affiliation[1]{organization={Levy Economics Institute of Bard
College},city={Annandale-on-Hudson,
NY},country={USA},countrysep={,},postcodesep={}}
\affiliation[2]{organization={Universidad Católica Boliviana},city={La
Paz},country={Bolivia},countrysep={,},postcodesep={}}
\affiliation[3]{organization={The World Bank},city={Washington,
D.C.},country={USA},countrysep={,},postcodesep={}}

@@

While this specification imposes a strong assumption on the DGP, it has
two advantages over the standard quantile regression model. First,
because the location-scale model can be identified globally, with only a
single parameter (\(q_\tau\)) requiring local estimation, this
estimation approach will be more efficient than the standard quantile
regression model \citep{zhao2000}. Second, under the assumption that
\(X\gamma\) is strictly positive, the model will produce quantile
coefficients that do not cross \citep{he1997}.

@@

@@

To show the performance of the extended strategy, we implement a small
simulation study. We consider a simple model with a single explanatory
variable \(x\). In contrast with MSS, we consider a two-way fixed effect
structure. For this exercise, we consider the following data-generating
process:

\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
\]

where \(\alpha_{1i}\sim \chi^2(1)\), \(\alpha_{2i} \sim \chi^2(1)\), and
\(x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))\), with
\(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
\(\varepsilon_i\) is assumed to follow a centered \(\chi^2\)
distribution.\footnote{Specifically we assume
  \(\varepsilon=\frac{r_i}{5}-1\), where \(r_i\) follows a chi-squared
  distribution such that \(r_i \sim \chi^2(5)\). Simulations under the
  assumption of normal errors are available upon request.} We assume
that there are 50 mutually exclusive groups for each set of fixed
effects. Observations are assigned to each subgroup randomly using a
uniform distribution between 1 and 50.

To assess the alternative Standard error estimators, we consider a
second data-generating process where the error term is correlated within
clusters. For this, we assume observations are assigned ramdomly to 100
mutually exclusive groups, which are independent from the fixed effect
groups. In this setup the data-generating process is:

\[\begin{aligned}
y_i &= \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} )*\kappa_i \\
\kappa_i &= inv-\chi^2_5(r_{i})/5-1 \\
r_i &= \Phi((\sqrt{.25}*s_{i}+\sqrt{.75}*s_{g}))
\end{aligned}
\]

where \(s_{i}\sim N(0,1)\) and \(s_{g}\sim N(0,1)\), are errors that
vary across individuals \(i\) or across clusters \(g\). \(\Phi()\) is
the cumulative distribution function of a normal distribution, and
\(inv-\chi^2_5()\) is the inverse function for a Chi-2 distribution with
5 degrees of freedom. With this setup, we generate an error structure
with a strong intra-cluster correlation, but without affecting the model
specification assumption.\footnote{We do not consider the case of
  misspecification of the scale model because that change would not only
  have an impact on the standard errors, but also affect the bias of the
  estimated coefficients}

We consider sample sizes of 500, 1000, 2000, and 4000 observations,
which implies an average of 10, 20, 40, and 80 observations per group.
The model is estimated using the location-scale model with
heteroskedastic linear errors and we report the coefficients for the
25th and 75th quantiles. We run this excercise 5000 times.
Table~\ref{tbl-sim1} reports the bias, simulated standard error, and
mean squared error, using the first data generation structure only. We
also report the results obtained using an adaptation bias-corrected
estimator based on the split-panel jackknife estimator proposed by
\citet{dhaene2015}.\footnote{For the implementation, we first estimate
  the model using the full sample, then randomly assign each observation
  into one of two groups, and finally reestimate the quantile
  coefficients for each group. The bias-corrected estimator is then
  obtained as
  \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)\).}
These results are labeled JKC.

Similar to the findings in MSS, we find that while the estimator
presents a substantial bias when the sample is small (\(N=500\)), this
bias shrinks as the sample size increases. As MSS describes, the bias
seems to be proportional to the sample size, or more precisely to the
average number of observations per sub-group. Interestingly, the
bias-corrected estimator presents an almost 0 bias for the 25th
percentile, even when the samples are small. In contrast, when
considering the 75th percentile, the simple estimator shows smaller bias
than the Jacknife estimator.{[}\^{}88: This is also consistent with
simulations with a single fixed effect{]} In either case, despite the
bias reduction obtained using the JKC estimator, the standard errors are
larger than without correction. For the 25th quantile, the reduction in
bias is large enough to produce a smaller Mean Squared Error (MSE) than
the simple estimator. This is similar to the results of MSS.

@@

\begin{tabular}{l*{6}{c}cccccccccccc}
\hline
            &     \multicolumn{3}{c}{N = 500}   &     \multicolumn{3}{c}{N = 1000}            \\
            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
\hline
q25         &            &            &            &            &            &            \\
mmqreg      &       0.169&       0.267&       0.099&       0.092&       0.172&       0.038\\
jkc         &       0.048&       0.318&       0.104&       0.014&       0.189&       0.036\\
\hline
q75         &            &            &            &            &            &            \\
mmqreg      &      -0.050&       0.446&       0.202&      -0.010&       0.310&       0.096\\
jkc         &       0.048&       0.546&       0.301&       0.018&       0.339&       0.115\\
\hline
            &     \multicolumn{3}{c}{N = 2000}   &     \multicolumn{3}{c}{N = 4000}            \\
            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
\hline
q25         &            &            &            &            &            &            \\
mmqreg      &       0.050&       0.119&       0.017&       0.026&       0.084&       0.008\\
jkc         &       0.006&       0.126&       0.016&       0.003&       0.087&       0.008\\
\hline
q75         &            &            &            &            &            &            \\
mmqreg      &       0.001&       0.215&       0.046&       0.003&       0.151&       0.023\\
jkc         &       0.006&       0.222&       0.049&       0.002&       0.154&       0.024\\
\hline
\multicolumn{7}{p{.7\textwidth}}{ \footnotesize Note: mmqreg - The proposed estimator. 
JKC-Jacknife Bias Corrected Estimator. SE- Simulated Standard Error.
MSE - Mean Squared Error. Mean bias is the difference 
between the estimated coefficient and the analytical true value. }\\
\end{tabular}

@@

To evaluate the performance of the different standard errors, we present
bias, 95\% coverage of the biased corrected estimates, as well as the
simulated standard errors, average and median of the standard errors
obtained using the GLS, robust SE, and clustered standard SE.
Table~\ref{tbl-sim2} considers the d.g.p. without intra-cluster
correlation, while Table~\ref{tbl-sim3} considers the d.g.p. that
induces intra-cluster correlations. All simulations consider 5000
repetitions.

The bias magnitude in Table~\ref{tbl-sim2} and Table~\ref{tbl-sim3} is
comparable to those observed in Table~\ref{tbl-sim1}, with simulated
standard errors that show to be slighly larger when we allow for
intra-cluster correlations, just as expected. When assuming there is no
need to clustered standard errors (Table~\ref{tbl-sim2}), the coverage
associated to GLS standard errors is above 95\% when the samples are
small, but it approximates to 95\% as the sample size increases. On the
other and, the coverage rates associated to Robust Standard errors are
closer to 90\%, albeit increasing slighly for larger samples.

One of the main reason that the GLS-Standard errors achieve higher than
expected rates of coverage may be related to the fact that the Standard
error estimator is very sensitive to near zero predictions from the
scale model. As shown in Table~\ref{tbl-sim2}, average and median GLS-SE
are considerably larger than the simulated standard errors when the
sample are small. While robust standard errors are less sensitive to
this problem, producing more stable results, they tend to underestimate
the magnitude of the true standard errors in small samples. This
translates into the lower coverage rates.

\caption{\label{tbl-sim2}95\% Coverage Ratio, and Standard Error
Estimation: No Intra-cluster Correlation}

\begin{tabular}[hbt!]{l*{10}{c}cccccccccccccccccccc}
\hline 
            &      \multicolumn{4}{c}{Q25}   &      \multicolumn{4}{c}{Q75}   &\\
    N        &  =500& =1000 & =2000     &    =4000 &  =500& =1000 & =2000     &   =4000 & \\
\hline
Bias     &       0.173&       0.096&       0.050&       0.026&      -0.040&      -0.008&       0.003&       0.003\\
Sim SE         &       0.268&       0.171&       0.118&       0.084&       0.443&       0.314&       0.219&       0.153\\
Mean GLS SE      &1.9e7&       0.830&       0.401&       0.084&7.3e7 &       1.876&       4.259&       0.156\\
Median GLS SE     &       0.495&       0.215&       0.123&       0.083&       1.037&       0.429&       0.225&       0.152\\
CR95\%        &       0.988&       0.980&       0.958&       0.948&       0.991&       0.977&       0.967&       0.952\\
Mean Rbst SE     &       0.224&       0.159&       0.112&       0.080&       0.353&       0.269&       0.199&       0.144\\
CR95\%       &       0.892&       0.928&       0.939&       0.932&       0.875&       0.904&       0.927&       0.936\\
\hline 
%Mean CLS SE    &       0.235&       0.162&       0.112&       0.079&       0.372&       0.274&       0.199&       0.143\\
%CR95\%       &       0.907&       0.930&       0.932&       0.930&       0.892&       0.905&       0.925&       0.932\\    
\end{tabular}

When we consider the presence of Intra-Cluster correlation,
Table~\ref{tbl-sim3}, we still observe similar problems with the GLS-SE,
albeit with high coverage rates. While Robust and Clustered Standard
errors are in average smaller than the Simulated Standard errors,
coverage rates are above 90\%. Clustered standard errors perform the
best only when the sample size is large, with Robust standard error
producing low Standard errors estimates.

\caption{\label{tbl-sim3}95\% Coverage Ratio, and Standard Error
Estimation: With Intra-cluster Correlation}

\begin{tabular}[hbt!]{l*{10}{c}cccccccccccccccccccc}
    \hline 
             &      \multicolumn{4}{c}{Q25}   &      \multicolumn{4}{c}{Q75}   &\\
             N        &  =500& =1000 & =2000     &    =4000 &  =500& =1000 & =2000     &   =4000 & \\
   \hline
    Bias    &       0.180&       0.091&       0.053&       0.027&      -0.022&      -0.008&       0.003&       0.003\\
    Sim SE         &       0.299&       0.200&       0.141&       0.100&       0.503&       0.352&       0.253&       0.182\\
    Mean GLS SE      &1.5e7&       1.053&       0.190&       0.093&6.0e7 &       1.332&       0.309&       0.167\\
    Median GLS SE      &       0.476&       0.215&       0.133&       0.092&       0.913&       0.384&       0.236&       0.165\\
    CR95\%      &       0.984&       0.963&       0.939&       0.928&       0.986&       0.963&       0.940&       0.925\\
    Mean Rbst SE    &       0.253&       0.179&       0.126&       0.089&       0.402&       0.303&       0.222&       0.160\\
    CR95\%       &       0.896&       0.916&       0.917&       0.915&       0.880&       0.905&       0.917&       0.906\\
    Mean CLS SE    &       0.252&       0.180&       0.130&       0.096&       0.397&       0.304&       0.228&       0.172\\
    CR95\       &       0.892&       0.915&       0.923&       0.935&       0.875&       0.902&       0.919&       0.928\\
    \hline 
\end{tabular}

Overall, the simulation study shows that using GLS-SE estimator may be
appropriate when the sample is relatively large. When there is suspected
presence of intra-cluster correlation, the use of clustered standard
errors is recommended in larger samples. However, when the sample is
small, the use of robust standard errors may be appropriate if GLS
standard errors when there is the risk of near-zero predictions from the
scale model.

@@

Furthermore, we have assessed the impact of intracluster correlation on
the performance of standard error estimations. Our findings emphasize
the importance of using appropriate standard error estimators to ensure
accurate inference. In particular, we find that GLS standard errors are
biased when when the scale model predictions are close to zero or
negative, and that Robust and clustered standard errors are more stable
in those scenarios. Clustered Standard errors perform the best in the
presence of intra-cluster correlation, but the advantage is only evident
when the sample size is large.

Finally, we have illustrated the application of our extended methodology
using data from \citet{persson_economic_2005}. Our results are
consistent with those reported in \citet{mss2019}, and we are able to
provide robust and clustered standard errors for the location and scale
coefficients. We find that the GLS standard errors are almost twice as
large as the robust and clustered standard errors, which is consistent
with the results from our simulation study. Nevertheless, there is no
drastic change in the original conclusions.

@@

\begin{itemize}
\tightlist
\item
  \texttt{mmqreg} in Stata:
  \texttt{net\ install\ mmqreg,\ from(https://friosavila.github.io/stpackages)}
\item
  \texttt{mmqreg} in R: Available on GitHub
  (https://github.com/friosavila/mmqreg)
\end{itemize}
